Automated Residual Plot Assessment with the R Package autovi and the Shiny App autovi.web

### 2024-11-26 autovi_paper.qmd
A couple of comments

The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system. This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding. While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package.

>>>>

The `autovi` package is built on the `bandicoot` object-oriented programming (OOP) system [@bandicoot], marking a departure from R’s traditional S3 generic system. This OOP architecture enhances flexibility and modularity, allowing users to redefine key functions through method overriding XXX I think the technical term is overloading? XXX. While similar functionality could be achieved using R’s S3 system with generic functions, the OOP framework offers a more structured and extensible foundation for the package. XXX Not sure if this last sentence is necessary XXX
